Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex
a folder for figures

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

\subsection{Procedure}\label{procedure}

\subsubsection{Data Pre-processing and Features}

@@

\subsubsection{Embedding Layer}
An embedding layer is used to compute a word embedding $W: words \mapsto \mathbb{R}^{n}$ which is a function mapping words of a language to a high dimensional vectors which are continuous, distributed representation of the vocabulary words with good semantic properties. The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.

\subsubsection{Discriminative Model}

%\subsubsection{Baseline System}
We construct two baseline systems, one to classify the journals based on the
content of the articles and the second on their authors. Identical architectures are used for both the baseline
systems. The baseline system is a recurrent neural network with one hidden Long
Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
both the embedding layer and the LSTM was fixed to 128. The output layer is a
softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \href{References}{{[}6{]}}

%\subsubsection{Proposed System}
%The procedure is quite straight-forward. While part of the team worked on
%building our tailored dataset, the other half worked on the model definition
%and training procedure.

%Once every pre-requisite is available, we trained the first encoder $E_1$
%(implemented as a recurrent neural network) to build the embedding $V_1$. Since
%we only dealt with a relatively simple classification task, our decoder $D_1$
%was simply a fully connected multi-layer perceptron. They were jointly trained
%end-to-end by propagating the gradients through the embedding from $D_1$ to
%$E_1$.

%The second training step was to train the second encoder $E_2$. Again, we also
%performed training end-to-end, but specifically did not propagate the gradients
%through $E_1$.

\subsection{Evaluation}

\section{Results}\label{results}
\subsection{Baseline}
\subsection{Proposed System}

\section{Discussion}\label{discussion}

\section{References}\label{References}

@@

  http://arxiv.org/abs/1409.3215
\item
  Grammar as a Foreign Language, Vinyals \& al,
  http://arxiv.org/abs/1412.7449
\item
  Deep Fragment Embeddings for Bidirectional Image Sentence Mapping,
  Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf

\item Adaptive Subgradient Methods for Online Learning and Stochastic Optimization, Ducih \& al, http://www.jmlr.org/papers/volume12/duchi11a/duchi11a.pdf
\end{enumerate}

>>>>

%\section{Method}\label{method}

\section{Database}\label{materials}

We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. Each json object 
contains the flollowing fields:
source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
\begin{itemize}
\item source: A string identifier of the newspaper from which the article was extracted.
\item url: The full URL from which the article was extracted.
\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
\item title: The title of the article. 
\item author: The author of the article.
\item content: The content of the article.
\end{itemize}

\section{Procedure}\label{procedure}

\subsection{Data Pre-processing and Features}

@@

\subsection{Neural Network Architecture}
\subsubsection{Embedding Layer}
An embedding layer is used to compute a word embedding $W: words \mapsto \mathbb{R}^{n}$ which is a function mapping words of a language to a high dimensional vectors which are continuous, distributed representation of the vocabulary words with good semantic properties. The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.
\subsection{Baseline System}
Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles. Identical architectures are used for both the baseline systems. The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of both the embedding layer and the LSTM was fixed to 128. The output layer is a soft-max layer with 14 dimension for each class representing each journal. Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).

\subsection{Proposed System}
The procedure is quite straight-forward. While part of the team worked
on building our tailored dataset, the other half worked on the model
definition and training procedure.

Once every pre-requisite is available, we trained the first encoder
$E_1$ (implemented as a recurrent neural network) to build the embedding
$V_1$. Since we only dealt with a relatively simple classification task,
our decoder $D_1$ was simply a fully connected multi-layer perceptron.
They were jointly trained end-to-end by propagating the gradients
through the embedding from $D_1$ to $E_1$.

The second training step was to train the second encoder $E_2$. Again,
we also performed training end-to-end, but specifically did not
propagate the gradients through $E_1$.

\subsection{Evaluation Metrics}\label{evaluation}

\section{Results}\label{results}
\subsection{Baseline}
\subsection{Proposed System}
\section{Discussion}\label{discussion}

\section{References}\label{references}

@@

  http://arxiv.org/abs/1409.3215
\item
  Grammar as a Foreign Language, Vinyals \& al,
  http://arxiv.org/abs/1412.7449
\item
  Deep Fragment Embeddings for Bidirectional Image Sentence Mapping,
  Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf
\end{enumerate}
